### 2015-07-08 abstract.tex

\vspace{-\belowdisplayskip}
\vspace{-\abovedisplayskip}
\smallskip

@@

% Even with the space manipulation above, we need to cheat a little
\enlargethispage{2\baselineskip}
Scientific discovery at the exascale will not be possible without significant
new research in the management, storage and retrieval over the long lifespan
of the large amounts of data that will be produced.
In this project we will
demonstrate novel techniques to  facilitate efficient mapping of data
objects, even partitioning individual variables, from
the user space onto multiple storage tiers, and enable application-guided
data reductions and transformations to address capacity and bandwidth
bottlenecks. 
Our goal in this project is
to address the associated Input/Output (I/O) and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes; which is associated with {\bf theme two} of the Funding Opportunity Announcement. To that end, we will build on the
capabilities offered by Adaptable I/O System (ADIOS) and DataSpaces at ORNL that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL, Rutgers), file system (SNL, UCSC) and storage (UCSC), and connects and
coordinates these key storage components in a seamless fashion.

>>>>

%\vspace{-\belowdisplayskip}
\vspace{-\abovedisplayskip}
\smallskip

@@

% Even with the space manipulation above, we need to cheat a little
\enlargethispage{2\baselineskip}
Scientific discovery at the exascale will not be possible without significant
new research in the management, storage and retrieval over the long lifespan
of the extreme amounts of data that will be produced.
In this project we will
demonstrate novel techniques to  facilitate efficient mapping of data
objects, even partitioning individual variables, from
the user space onto multiple storage tiers, and enable application-guided
data reductions and transformations to address capacity and bandwidth
bottlenecks. 
Our goal in this project is
to address the associated Input/Output (I/O) and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into mission
critical scientific processes; which is associated with {\bf theme two} of the Funding Opportunity Announcement. To that end, we will build on the
capabilities offered by Adaptable I/O System (ADIOS) and DataSpaces at ORNL that provide I/O abstractions
and services, the Sirocco peer-to-peer file system at
Sandia and the object storage and annotation expertise of UC Santa Cruz, to
explore application and multi-tier storage aware data management
solutions.    This project
brings together a  team with strong expertise in I/O middleware (ORNL, Rutgers), file system (SNL, UCSC) and storage (UCSC), and connects and
coordinates these key storage components in a seamless fashion.

### 2015-07-08 coverpage.tex

%% Application/Institution
\begin{tabbing}
\hspace*{10mm} \= \makebox[65mm][l]{\textbf{Applicant Institution:}} \= Oak Ridge National Laboratory \\
\>  \>PO BOX 2008 MS6057 Oak Ridge TN 37831-6057\\
\end{tabbing}

@@

%% Lead PI name, telephone number, email:
\begin{tabbing}
\hspace*{10mm} \= \makebox[65mm][l]{\textbf{Lead Principal Investigator:}} \=
\vrule height0.4pt depth 0pt width 2.5in \\
\> \> Scott KIasky,  Distinguished Scientist \\
\> \> Oak Ridge National Laboratory \\
\> \> Computer Science and Mathematics Division \\
\> \> Oak Ridge, TN 37831-6057 \\
\> \> (T) 865-241-9980 (Fax) 865-241-4811 \\
\> \> klasky@ornl.gov
\end{tabbing}

@@

%% Adminisrative Point of Contact name, telephone number, email:
\begin{tabbing}
\hspace*{10mm} \= \makebox[65mm][l]{\textbf{Administrative Point of Contact:}} \=
\vrule height0.4pt depth 0pt width 2.5in \\
\> \> Tammy Reed \\
\> \> Oak Ridge National Laboratory \\
\> \>Computer Science and Mathematics Division \\
\> \> Oak Ridge, TN 37831-6057 \\
\> \> (T) 865-574-1936 (Fax) 865-241-4811\\
\> \> tsr@ornl.gov
\end{tabbing}

@@

\begin{tabbing}
\hspace*{10mm} \= \makebox[80mm][l]{\textbf{Program Announcement Number:}} \= LAB 15-1338 \\
\> \textbf{DOE/Office of Science Program Office:} \> Office of Advanced Scientific Computing Research\\
\> \textbf{DOE/Office of Science Program Office}  \> \\
\> \makebox[70mm][r]{\textbf{Technical Contact:}} \> Lucy Nowell\\
\end{tabbing}

>>>>

%% Application/Institution
\begin{tabbing}
\hspace*{10mm} \= \makebox[65mm][l]{\textbf{Applicant Institution:}} \= Oak Ridge National Laboratory \\
\>  \>1 Bethel Valley Road\\
\> \> Oak Ridge Tennessee 37831-6057\\
\end{tabbing}

@@

%% Lead PI name, telephone number, email:
\begin{tabbing}
\hspace*{10mm} \= \makebox[65mm][l]{\textbf{Lead Principal Investigator:}} \=
\vrule height0.4pt depth 0pt width 2.5in \\
\> \> Scott Klasky,  Distinguished Scientist \\
\> \> Oak Ridge National Laboratory \\
\> \> Computer Science and Mathematics Division \\
\> \> Oak Ridge, Tennessee 37831-6057 \\
\> \> (T) 865-241-9980 (Fax) 865-241-4811 \\
\> \> Email: klasky@ornl.gov
\end{tabbing}

@@

%% Adminisrative Point of Contact name, telephone number, email:
\begin{tabbing}
\hspace*{10mm} \= \makebox[65mm][l]{\textbf{Administrative Point of Contact:}} \=
\vrule height0.4pt depth 0pt width 2.5in \\
\> \> Barney Maccabe \\
\> \> Oak Ridge National Laboratory \\
\> \> Computer Science and Mathematics Division \\
\> \> Oak Ridge, TN 37831-6057 \\
\> \> (T) 865-241-6504 \\
\> \> Email: maccabe@ornl.gov
\end{tabbing}

@@

\begin{tabbing}
\hspace*{10mm} \= \makebox[65mm][l]{\textbf{Program Announcement Number:}} \= LAB 15-1338\\
\> \textbf{PAMS Tracking No.:}			    \> 0000219877\\
\> \textbf{DOE/Office of Science Program Office:} \> Office of Advanced Scientific Computing Research\\
\>									    \> Storage Systems and Input/Output for Extreme Scale Science\\
\> \textbf{DOE/Office of Science Program Office}  \> \\
\> \makebox[64mm][r]{\textbf{Technical Contact:}} \>  Lucy Nowell\\
\\
\> \textbf{Research Area:} \>Scalable Storage Software Infrastructure

\end{tabbing}

### 2015-07-08 narrative/data-description.tex

A key insight in this proposed project has been the increased interaction of
the application with the storage system.
The user would like to have the ability to obtain information about, and even
negotiate with the system to determine what
level of QofS is possible given
a prospective set of I/O operations and current state of the system, so that
they can then make decisions about what data to access when.
%for example is less than what they desire and will then place in a certain set
%of rules which the system can make autonomic decisions to help decide what
%should be done.
Towards this end, we propose to
address the QoS requirements by providing the application with mechanisms to
specify the quality of I/O service, interrogate the storage system, and react
to the responses. Guided by our past work we propose to explore the design of
mechanisms for this purpose.

Our research will address the following questions:
1) How can users interact with the storage system efficiently?
2) How can users express their intentions into actionable items which can take place in the middleware and/or storage layer?
3) How can users annotate data with a utility metric?

>>>>

A key insight in this proposed project has been the increased interaction of
the application with the storage system.
The user would like to have the ability to obtain information about, and even
negotiate with the system to determine what
level of QoS is possible given
a prospective set of I/O operations and current state of the system, so that
they can then make decisions about what data to access when.
%for example is less than what they desire and will then place in a certain set
%of rules which the system can make autonomic decisions to help decide what
%should be done.
Towards this end, we propose to
address the QoS requirements by providing the application with mechanisms to
specify the quality of I/O service, interrogate the storage system, and react
to the responses. Guided by our past work we propose to explore the design of
mechanisms for this purpose.

Our research will address the following questions:
1) How can users interact with the storage system efficiently?,
2) How can users express their intentions into actionable items which can take place in the middleware and/or storage layer?, and
3) How can users annotate data with a utility metric?

### 2015-07-08 narrative/data-reduction.tex

Ideally, the scientists would perform the entire analysis stage {\em in situ}
to extract the relevant information and in so doing would effectively
circumvent the large data issue completely.  The catch, of course, is that this
is unlikely to be possible since, by their nature, large scale simulations aim
to discover new information that is often hidden in the form of higher order
effects amongst the data deluge. In particular, this means if data thinning or
truncation is applied willy nilly then one is in danger of effectively throwing
out the information one is seeking. It would seem that one cannot store the
entire data set in an easily accessible source, due to sheer size, yet one
cannot reduce it prior to archival without risking losing the information one
is trying to extract.  Viewed in this way, the problem would appear
intractable. However, the above discussion fails to recognize that much of the
data is redundant in an information theoretic sense.  That is to say, the
amount of information contained in the dataset is often significantly less than
the amount of data.  The difficulty stems from the fact that one does not know
about this redundancy in advance \emph{without the benefit of priori
knowledge}. This knowledge can often be provided by the user or can be acquired
through experience of dealing with differing runs of the same code.

>>>>

Ideally,  scientists would like to perform the entire analysis stage {\em in situ}
to extract the relevant information and in so doing would effectively
circumvent the large data issue completely.  The catch, of course, is that this
is unlikely to be possible since, by their nature, large scale simulations aim
to discover new information that is often hidden in the form of higher order
effects amongst the data deluge. In particular, this means if data thinning or
truncation is applied haphazardly then one is in danger of effectively throwing
out the information one is seeking. It would seem that one cannot store the
entire data set in an easily accessible source, due to sheer size, yet one
cannot reduce it prior to archival without risking losing the information one
is trying to extract.  Viewed in this way, the problem would appear
intractable. However, the above discussion fails to recognize that much of the
data is redundant in an information theoretic sense.  That is to say, the
amount of information contained in the dataset is often significantly less than
the amount of data.  The difficulty stems from the fact that one does not know
about this redundancy in advance \emph{without the benefit of priori
knowledge}. This knowledge can often be provided by the user or can be acquired
through experience of dealing with differing runs of the same code.

### 2015-07-08 narrative/intro.tex

%
%\section{Scalable Storage Software Infrastructure}
%Our focus in this proposal is in Theme 2: {\em Scalable Storage Software Infrastructure} 
%We will focus on a state of the art SSIO solution to solve problems which researchers are 
%beginning to face and will make science on exascale systems
%problematic without new insights and solutions.
Our proposal will be responsive to Theme 2: {\em Scalable Storage Software Infrastructure} of the call, as summarize in Table~\ref{tab:call}.

@@

This forced the team to carefully scrutinize the large amount of data to be generated and save only the very most important pieces. Further, they had to break this greatly reduced data into two categories: first data they thought they would need to access while the simulation was running or shortly thereafter, and second data they would need after the whole campaign was finished. The former category would be stored on disk, and the later would be archived. Additionally, they needed to figure out how to efficiently retrieve these different categories of data for post-processing, analysis and visualization.

@@

We  examine the research challenges from the perspective of
%
(1) the scientist who runs the exascale simulation,
%
(2) the Storage System and I/O layer which needs to negotiate between all of
the users, and finally
%
(3) the user of the system who is attempting to understand the data
produced by a set of simulations.

\paragraph{Simulation Perspective}
\label{subsec:sim-perspective}
The simulation scientist ideally should be able to
obtain an estimate of how much time will be required to write the data,
and how much storage space is available during the simulations lifetime.
Further, they would like Quality of Service assurances so that reactions
to varying bandwidth can be handled appropriately. Ideally, a set of
user-specified rules would allow the system to make autonomic decisions dynamically.
%

Central to our approach is giving users the ability to define the importance, or utility of their data.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or specific
subsets and pieces.
Research challenges include 1) an expressive and easy to use interface, 2) a model for the system supporting
autonomic decision for saving data using the user-defined importance and utility of data, and 3) the interface between
the system and the back-end storage across both single, and multiple running applications.

@@

One of our  research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, an it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
%We will use learning techniques to automatically migrate data
%sub-objects across the hierarchy as well as to eventually evict data which is
%large and has very low utility.

>>>>

%
%\section{Scalable Storage Software Infrastructure}
%Our focus in this proposal is in Theme 2: {\em Scalable Storage Software Infrastructure} 
%We will focus on a state of the art SSIO solution to solve problems which researchers are 
%beginning to face and will make science on exascale systems
%problematic without new insights and solutions.
Our proposal will be responsive to Theme 2: {\em Scalable Storage Software Infrastructure} of the call, as summarized in Table~\ref{tab:call}.

@@

This forced the team to carefully scrutinize the large amount of data to be generated and save only the very most important pieces. Further, they had to break this greatly reduced data into two categories: first data they thought they would need to access while the simulation was running or shortly thereafter, and second, data they would need after the whole campaign was finished. The former category would be stored on disk, and the later would be archived. Additionally, they needed to figure out how to efficiently retrieve these different categories of data for post-processing, analysis and visualization.

@@

We  examine the research challenges from the perspective of:
%
(1) the scientist who runs the exascale simulation,
%
(2) the Storage System and I/O layer which needs to negotiate between all of
the users, and finally
%
(3) the user of the system who is attempting to understand the data
produced by a set of simulations.

\paragraph{Simulation Perspective}
\label{subsec:sim-perspective}
The simulation scientist ideally should be able to
obtain an estimate of how much time will be required to write the data,
and how much storage space is available during the simulations lifetime.
Further, they would like Quality of Service (QoS) assurances so that reactions
to varying bandwidth can be handled appropriately. Ideally, a set of
user-specified rules would allow the system to make autonomic decisions dynamically.
%

Central to our approach is giving users the ability to define the importance, or utility of their data.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or specific
subsets and pieces.
Research challenges include: 1) an expressive and easy to use interface, 2) a model for the system supporting
autonomic decision for saving data using the user-defined importance and utility of data, and 3) the interface between
the system and the back-end storage across both single, and multiple running applications.

@@

One of our  research objectives is to understand how the
storage system can interact with the middleware   so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. We need to maintain 
QoS and therefore, be able to provide fuzzy estimates of the time it will take to write/read data from
the different layers to inform any migration/eviction decisions, and it
is also critical that the storage system can manage (discover and retrieve) the data across all of the
layers automatically, without user intervention. 
%We will use learning techniques to automatically migrate data
%sub-objects across the hierarchy as well as to eventually evict data which is
%large and has very low utility.

### 2015-07-08 narrative/naming-service.tex
tight itemize, tight enumerate

Hierarchical Storage Management (HSM) systems~\cite{blaze:1992:hsm} offer a
strict caching approach for managing different storage capacities trading off
performance for capacity.  By maintaining a single namespace across all tiers,
it is possible to list a single directory view with files stored at different
tiers. While this approach to managing multi-tier storage works for whole files
that fit on single logial devices, it is far from ideal for scientific
simulations.

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time tradeoff reuqires additional
metadata.  Providing this functionality requries the naming service be able to
both return a list of data versions and an indication of data quality. This
will be combined with a retrieval time estimate for each verstion by the
middleware to determine what data version should be retrieved.  This estimate
will be disucssed elsewhere in this proposal.

@@

\paragraph{Approach:}
Our goal with this proposal is to offer a similar capability but with a finer
granularity leveraging the inner structure of scientific data. It must also
handle data discovery efficiently for cases where data is spread across several
storage layers or some of those pieces may have migrated based on system
pressures or user or system policies. Instead of a single file, such as might
be used to store an entire timestep output for a simulation, we will
demonstrate a metadata service with naming at the science variable level, but
with an associated list of all of the variable pieces and potentially different
versions stored throughout the storage system. By shifting to a finer-grained
approach, we will enable more effective use of close/fast/small storage tiers
and prioritize objects with high importance.  Traiditional HSM stores an entire
file on a tier making room if insufficient space is available.  With this shift
to a partial variable granularity, a 1 PB output with 500 GB of ``high
interest'' data can limit this costly tier usage to just 500 GB greatly
improving storage availability in the close/fast/small tier and focus
performance/capacity costs to get the most science from from the platform.  By
only placing ``high interest'' data in the close/fast/small tier, we will
effectively reduce pressure forcing data migration hurting both writing
performance and the later data analytics required for generating scientific
insights.  Sirocco identifies a data segment using a
contaier/object/fork/address tuple that can have associated attributes. We will
both add a special attribute indicating that this record is of ``high
interest'' as well adapting the migration mechanisms to use this attribute, if
present, to strongly encouraging keeping the record in close/fast/small storage
as long as possible.

@@

\begin{enumerate}

@@

\end{enumerate}

>>>>

Hierarchical Storage Management (HSM) systems~\cite{blaze:1992:hsm} offer a
strict caching approach for managing different storage capacities trading off
performance for capacity.  By maintaining a single namespace across all tiers,
it is possible to list a single directory view with files stored at different
tiers. While this approach to managing multi-tier storage works for whole files
that fit on single logical devices, it is far from ideal for scientific
simulations.

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time tradeoff requires additional
metadata.  Providing this functionality requires the naming service be able to
both return a list of data versions and an indication of data quality. This
will be combined with a retrieval time estimate for each version by the
middleware to determine what data version should be retrieved.  This estimate
will be discussed elsewhere in this proposal.

@@

\paragraph{Approach:}
Our goal with this proposal is to offer a similar capability but with a finer
granularity leveraging the inner structure of scientific data. It must also
handle data discovery efficiently for cases where data is spread across several
storage layers or some of those pieces may have migrated based on system
pressures or user or system policies. Instead of a single file, such as might
be used to store an entire timestep output for a simulation, we will
demonstrate a metadata service with naming at the science variable level, but
with an associated list of all of the variable pieces and potentially different
versions stored throughout the storage system. By shifting to a finer-grained
approach, we will enable more effective use of close/fast/small storage tiers
and prioritize objects with high importance.  Traditional HSM stores an entire
file on a tier making room if insufficient space is available.  With this shift
to a partial variable granularity, a 1 PB output with 500 GB of ``high
interest'' data can limit this costly tier usage to just 500 GB greatly
improving storage availability in the close/fast/small tier and focus
performance/capacity costs to get the most science from from the platform.  By
only placing ``high interest'' data in the close/fast/small tier, we will
effectively reduce pressure forcing data migration hurting both writing
performance and the later data analytics required for generating scientific
insights.  Sirocco identifies a data segment using a
contaier/object/fork/address tuple that can have associated attributes. We will
both add a special attribute indicating that this record is of ``high
interest'' as well adapting the migration mechanisms to use this attribute, if
present, to strongly encouraging keeping the record in close/fast/small storage
as long as possible.

@@

\begin{tightEnumerate}

@@

\end{tightEnumerate}

### 2015-07-08 narrative/qos.tex

\paragraph{Related Work:} On current HPC systems, absolute IO performance
guarantees are not possible. Previous work \cite{lofstead:2010:io-variability,liu_hotstorage} 
from this project team uses a client-assisted approach to mitigate IO variablity.
Existing efforts on scheduing resources~\cite{thapaliya:2014:io-cop,dorier:2014:calciom} attempt to offer
admission control to maximize storage performance. Unfortunately, these efforts
are limited to participating applications and only applications from a single
platform. For this approach to be effective, the storage system must offer an
approach that handles clients from all connected platforms and does not
require modification to use new storage access APIs. By using a priority
tagging system, we will offer defaults suitable for all applications that can
be informed by simple extensions to the job scheduler or more advanced
management through new APIs.

>>>>

\paragraph{Related Work:} On current production HPC systems, absolute IO performance
guarantees are not possible. Previous work \cite{lofstead:2010:io-variability,liu_hotstorage} 
from this project team uses a client-assisted approach to mitigate IO variablity at scale (100,000-core).
Recently server side QoS scheduling has also been studied for HPC applications \cite{Dai:2014}.
However, the key hurdle of scalability has not been solved.
Existing efforts on scheduing resources~\cite{thapaliya:2014:io-cop,dorier:2014:calciom} attempt to offer
admission control to maximize storage performance. Unfortunately, these efforts
are limited to participating applications and only applications from a single
platform. For this approach to be effective, the storage system must offer an
approach that handles clients from all connected platforms and does not
require modification to use new storage access APIs. By using a priority
tagging system, we will offer defaults suitable for all applications that can
be informed by simple extensions to the job scheduler or more advanced
management through new APIs. On the other hand, storage QoS has been
studied for enterprise applications and systems \cite {Gulati:2007,Gulati:2010,Gulati:2012}
in virtualized environments. It is not straightforward to adapt these solutions
to HPC storage systems because of the scalability and efficiency concerns, despite
they achieved very good performance isolations.

### 2015-07-08 other-support/lofstead-cp.tex

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= Scalable I/O Services\\
Source of Support           \>: \> NNSA Advanced Simulation and Computing Program\\
Award Amount                \>: \> \$1000K/year to SNL\\
Period Covered              \>: \> 10/2014 -- 9/2014\\
Investigator Commitment     \>: \> 0.2 FTE
\end{tabbing}

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= ATDM Data Management Services\\
Source of Support           \>: \> NNSA Advanced Simulation and Computing Program\\
Award Amount                \>: \> \$9800K/year to SNL\\
Period Covered              \>: \> 10/2014 -- 9/2018\\
Investigator Commitment     \>: \> 0.25 FTE
\end{tabbing}

\begin{tabbing}
Project Title \hspace{5.5em}\=: \=  HOBBES: OS and Runtime Support For Application Composition\\
Source of Support           \>: \> 2013 DOE Exascale Operating Systems and Runtimes\\
Award Amount                \>: \> \$340K/year to SNL\\
Period Covered              \>: \> 8/2013 -- 7/2016\\
Investigator Commitment     \>: \> 0.35 FTE
\end{tabbing}

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= High-Performance Decoupling of Tightly-Coupled Data Flows\\
Source of Support           \>: \> DOE Scientific Data Management, Analysis and Visualization at Extreme Scale 2\\
Award Amount                \>: \> \$200K/year to SNL\\
Period Covered              \>: \> 8/2014 -- 7/2017\\
Investigator Commitment     \>: \> 0.2 FTE
\end{tabbing}

@@

%\begin{tabbing}
%Project Title \hspace{5.5em}\=: \= Code Coupling for Scalability and Robust Data Analytics\\
%Source of Support           \>: \> Sandia National Laboratories LDRD \\
%Award Amount                \>: \> \$600K/year to SNL\\
%Period Covered              \>: \> 8/2014 -- 7/2017\\
%Investigator Commitment     \>: \> 0.5 FTE
%\end{tabbing}

>>>>

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= Scalable I/O Services\\
Source of Support           \>: \> NNSA Advanced Simulation and Computing Program\\
Award Amount                \>: \> \$1000K/year to SNL\\
Period Covered              \>: \> 10/2014 -- 9/2014\\
Investigator Commitment     \>: \> 0.2 FTE\\
Research Performed          \>: \> Integrated Application Workflow infrastructure support\\
Overlaps                    \>: \> Focused on IAWs in general. This proposal looks at NVM impacts.\\
\end{tabbing}

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= ATDM Data Management Services\\
Source of Support           \>: \> NNSA Advanced Simulation and Computing Program\\
Award Amount                \>: \> \$9800K/year to SNL\\
Period Covered              \>: \> 10/2014 -- 9/2018\\
Investigator Commitment     \>: \> 0.25 FTE\\
Research Performed          \>: \> data warehouse for task-based programming system.\\
Overlaps                    \>: \> None.\\
\end{tabbing}

\begin{tabbing}
Project Title \hspace{5.5em}\=: \=  HOBBES: OS and Runtime Support For Application Composition\\
Source of Support           \>: \> 2013 DOE Exascale Operating Systems and Runtimes\\
Award Amount                \>: \> \$340K/year to SNL\\
Period Covered              \>: \> 8/2013 -- 7/2016\\
Investigator Commitment     \>: \> 0.35 FTE\\
Research Performed          \>: \> Application composition operating system support.\\
Overlaps                    \>: \> Example workflows that will be explored in this proposal.\\
\end{tabbing}

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= High-Performance Decoupling of Tightly-Coupled Data Flows\\
Source of Support           \>: \> DOE Scientific Data Management, Analysis and Visualization at Extreme Scale 2\\
Award Amount                \>: \> \$200K/year to SNL\\
Period Covered              \>: \> 8/2014 -- 7/2017\\
Investigator Commitment     \>: \> 0.2 FTE\\
Research Performed          \>: \> Develop generic workflow components for HPC\\
Overlaps                    \>: \> Example workflows that will be explored in this proposal.\\
\end{tabbing}

@@

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= SCADS: Scalable Deep Storage Hierarchy for Exascale Computing\\
Source of Support           \>: \> DOE Storage Systems and Input/Output for Extreme Scale Science\\
Award Amount                \>: \> \$176/year to SNL\\
Period Covered              \>: \> 10/2015 -- 9/2018\\
Investigator Commitment     \>: \> 0.25 FTE\\
Research Performed          \>: \> effective NVM placement and capacity for best end-to-end science throughput\\
Overlaps                    \>: \> None.\\
\end{tabbing}
